% vim: spell : ft=tex
\chapter{Preparation is Key}

Gorn woke after an unusually peaceful sleep.

``We know what we're doing,'' said Gorn, ``but 

``Talose River etc.``

yahyah etc.

I can't believed I've been roped into this. The stupid girl is probably lying to
me and she'll lead me to some organisation where they'll rob me or something
evil. Hmph, why am I trusting her? This is stupid. Stupid, stupid. I'm retired.
Never fought in a war. I'm useless. Protect her? How so? I couldn't protect my
own family. Pathetic. There's nothing for me to do for her.

...But, there's something I could do for me. I could try to set things right. I
won't deny that she's used the fact that I've--I've lost you, Sharah, but she
reminds me of you. There's something--something, like the big spot on her face
or the way her face widens when she smiles, that's just like you. And I need
you, Sharah. I always needed you. Trixie is... giving me a chance. To have you
once more. I... I won't deny, it's kinda weird... Grrrrraaaaah, is this OK? Will
Trixie hate me for these thoughts? Is it... is it just another weak way of
pretending everything is fine?

I don't know. But I made a decision. I'll stick with it.

Where are we even going, then? She was so vague in all her so called
'explanations'. Gave me more questions than I had before, hmph. I guess we're
start with Rushbar on the north road... then there's that river, whatever the
name is, which leads to... Selebar, that's it. But if we don't find anything
there, we'd have to go back the other way... Such a pain!
