\chapter{Accidents Happen}
% vim: spell : ft=tex

``G'morn...''

Many a time, in this small village of Pettle and in other cities far and wide
across the land, had there been girls as depressed as the one girl who sat
currently on the side of the road. Many a time throughout the world's history
had there been such world-weary retired veterans as the one now making his way
between the winding houses of the quaint Pettle.

Many a time, such people had seen each other, acknowledged one another, maybe
even spoken to the other if it was a nice day and the sun was shining bright and
moods were more sincere than normal. Even before had those people grown to like
the other and, for one reason or another, travel with them to far-away places
and live wondrous adventures and daring escapes.

But as much as those people may have tried, not one ever had adventures such as
the ones our two to-be-companions ended up having. What began as a misunderstood
greeting evolved into a strong and rather unlikely relationship.

``What?'' said a well-built, greying man. He shook his head to move a few
strands of knotted hair from in front of his eyes. Silver-white hair extended
from his scalp to his shoulder on all sides apart from most of his forehead. He
fixed a hard, but tired gaze on what he considered the offending party -- the
girl (a beggar, no doubt) who had greeted him.

``Oh, um, good morning to you, mister, um... sir.'' The girl scrambled for
words, not expecting a reply and quite honestly half-asleep. She was sitting
slightly lopsided with no surface to rest her back on, an empty basket lined
with white cloth laying to her side. Her messy dirt-brown hair was less
well-maintained than the man's, though a similar length. She looked to be young,
perhaps 14 years old. As she spoke, she looked up at the towering man in front
of her, then whipped back her head down, fearful of his penetrating gaze.

``Who are you to know my name?'' questioned the man, still maintaining a rather
intimidating stare.

``Yo-your name? I don't know your name.'' The girl looked up at the man.

``You just called it now.''

``But I just s-said good'morn.''

``Oh.'' The man fell silent for a moment. The girl noticed that his cheeks were
reddened. She lost her fear of the man and turned her head upwards to get a
proper view of him.

Now that an exchange had begun, both of them looked at the other properly for
the first time. The man noted many immediate features about the girl.

The most obvious was her terribly short hair, which appeared to have been cut
recently, and most definitely not washed for weeks. Thin blades of grass stuck
out of the front half of her head. Some parts of her hair were straight, some
were all tangled up with each other. Then her large blue eyes met his and he
suddenly felt very nostalgic, though he couldn't think why. The girl's face was
round and there were creases around her mouth, as if she smiled constantly
(clearly today was the exception). Her clothes were ragged, yet hardly marked
from dirt. He noted that she was thin, but not incredibly so.

The girl was eyeing the man at the same time. She wondered at his rare silver
hair, gawped at his visible scars, stared at his strong arms. His appearance was
of a normal person on who time had run its course; but then she noticed an
insignia on his upper arm. It was shaped like a shield with a cross in the
middle and a spear pointing upwards through the centre. Her eyes widened and her
mouth opened as she recalled what it meant.

``You're a soldier!'' she exclaimed.

``Long past are those days. I prefer to spend my time sitting in front of my
fire, simply relax--''

``You! You can help me! Can you--can I come with you back to your house?''

The girl's request was absurd, he knew. He prepared a short reply, then faltered
as he began to speak. The girl was looking intently at him, with sparkling eyes
and pleading hands. He knew not what she wanted, nor who she was -- and yet as
he paused he found it harder and harder to reject the seeming beggar girl. But
she was not begging for a positive answer, merely asking, hoping that her honest
request could be fulfilled. He was reminded of another girl, from another life:
one he had loved, one he could never let go of. His eyes drifted, then came
back, and no matter how hard he tried they wouldn't let him look directly at the
girl.

``I suppose I would have nothing against it. Come along if you must.'' he said,
rolling his eyes and trying to sound as reluctant for the idea as he could. He
felt a slight twinge of foolishness as he turned to continue home, but it was
largely numbed by the strange feeling that still lingered from when she asked
him.

\scenesep

The rest of the journey to the man's house continued in silence. Neither of the
two could think of much to say: the man was plenty busy feeling sheepish at
his behaviour and that he didn't even know the girl's name; and was she skipping
away, on the edge of jumping for joy just being able to follow him.

Soon enough they arrived at a huge house, seemingly in disrepair -- but the man
walked right up to the porch and pulled out a key. He called out without moving
his head (for his embarrassment had not worn off just yet), ``Oh, I believe I
never asked your name, little miss.''

``Yes, it's Trixie.'' What a strange name! he thought. ``What's yours?''

``Gorn.'' He paused. ``Gorn Markusson. Now let's get inside. My feet are cold.''

He ushered Trixie in through into a lobby room. Around her hung old portraits
and landscapes, made dull by the passage of time. The carpet was rough and had
faded into muddy browns and reds, which had in turn been made dirty brown by
coats of dust. Directly ahead of the entrance was a small cupboard against the
wall, with a big clock above it tick-tocking loudly to itself. The lobby fed off
into two corridors on either side of the cupboard. She felt that the house was
too big for one person to live in.

``Does anyone else live here?'' she asked to the air.

``No. It's... it's just me.'' Gorn sighed and his eyes lost focus again.

Now curiosity truly held Trixie captive. First she finds an old soldier, sitting
idle in a boring old hamlet like Pettle; now his house is creepy and quite
empty; then what could be over here? she thought. Slipping past Gorn, she took a
left into another room.

She gasped as a huge room came into view, extending ten metres inwards and three
across. The room lay almost utterly barren. A fireplace was situated in the
centre of the long wall opposite her, along with a rocking chair and a drinking
table with two chairs nearby. More portraits lined the marked walls, most
seeming to be soldiers or distinguished persons receiving awards. She could look
to the other end of the room and spy the dust in each corner. Such a big room,
and nothing in it! she wondered. It made her feel a little sad.

She skipped to one of the chairs and made herself comfortable before staring at
the framed portraits again. She could make out engraved names below the closer
ones. Lars Trencher, Yorcken and Droycken Gar'ram, Lord Jaggard the Strong-Armed
-- very manly names, Trixie thought, conjuring up images of ranks of muscular
men all wielding terrifying swords and shouting unintelligible war cries. Very
scary names too, she decided. Her eyes came to rest on a well-kept painting
which was surely made to stand out from the others. It depicted a tall,
confident man. His posture was straight-backed and proper, his proud face
showing no hints as to his feelings.  He held a downwards-facing rapier into his
chest so that it did not touch the ground, and there was a strange metal barrel
with a curved handle tucked into his trousers. Trixie looked closely, and saw
that his hair was greying at the roots.

``Tch.'' Trixie jerked her head towards to the sound -- Gorn had come in at that
moment. He walked over to the rocking chair and turned and sat on it in one
smooth, practiced motion.

``Didn't anyone teach you proper manners? Such rudeness to waltz around a
stranger's house without permission.''

``Oh, do forgive me! Your house is so very big and interesting, I couldn't sit
still.'' said Trixie earnestly.

``You have found your way into the sitting room, so I shan't take it further.''
He rubbed his chin. ``Now, let us forgo formalities -- you must tell me why you
wanted so badly to see this old run-down house of mine.''

``Um, yes, thank you. You see, my family lives here in the village, and my
brother is so terribly ill. He is too weak to work outside, so he can't earn any
money for us, and we can't buy enough food. We needed someone to ask passerbys
-- um, passers-bys?  -- for help or money, so I offered because people seem
weaker to requests from young girls.'' She grinned slyly, but Gorn stared
sternly back.  She hurried on with her story. ``But I kept falling asleep and
drifting off...  Then you came past and I saw the army badge on your jacket!''

``Why is my past of importance to you?'' Gorn bristled with quiet anger, tired
of her aimless story and certainly not enjoying the direction he believed that
the conversation was taking. Trixie continued.

``My mum said that there was an potions and elick-sures shop in the one of the
nearby cities. She doesn't know which one, but there must be some place which
would know how to help my brother! So please, could you ess-caught me there?''
She stumbled with some less common words, as if having been given a script on a
minute's notice.

``Ahah!'' exclaimed Gorn. ``So you wish for me to protect your fragile self on
the dangerous road to... somewhere?''

``That's right!'' answered Trixie gladly. He wondered how he managed to
understood her story more quickly than she did. ''You were in the army, right?
So you're strong! You could be my gar-dian!''

Now Gorn turned his head down and sighed. He felt troubled and looked at the
portraits from his army days, but that made him feel sick. So he sat like this
for a minute, his head resting low on his hand. Trixie could see that his face
was stuck in this sad, yearning frown. She decided to do one final plead.

``Please, mister. We don't know what to do. No matter how much we ask, all the
a-po-the-carries wave us away. When we talked to the--the person who sells
medicine in the village and explained what was happening to my brother, she said
she hadn't a clue. Everyone doesn't know what's wrong with him and I'm scared
because he won't get better without help and he was always so nice to me and
everyone else and he's the most kind--'' Trixie broke off and put her head in
her hands, quietly sobbing.

Gorn knew that he was being manipulated here. Trixie was trying too hard: the
cracks in her voice sounded forced, and she was likely channelling whichever
emotions she believed would move him most effectively. But when he looked at
her, he was reminded of something. A figure mostly obscured in his mind; but
though he swore to himself that it was unclear, he didn't need any other hints
to tell him what he saw in the girl.

You see, Gorn had a tragic life twenty years ago as a father. Fathering a child
just as a war dug its roots into a neighbouring city, he was whisked into a
local regiment for training. As all men do, he was confident he would return
home in just a few short years and find his beautiful wife and child anxiously
awaiting him, to swamp him in tears and love. And to his surprise, his time in
the army was relatively short. After a one year each of training and service, he
returned to his home in Pettle -- to find that just a month after he left, a
bandit clan had torn through the peaceful village, sacking houses and slitting
throats. No one could tell him where his beloved had gone, or been taken. When
he heard this, he merely stood in place for a moment, then left for his house.
For two decades, not a day went by when he didn't cry for his loss: one that was
unjust and unfair, one which he could have prevented. He was never able to let
go of his old life: neither his dear wife, nor his sweet daughter who he loved
the most in the world.

A long time passed while Gorn stared at the young girl before him. He hadn't
expected to ever find himself in such a situation: for after his loss, Gorn had
given up on adventuring. He became somewhat of a recluse, trapping himself in an
oversized house for one and surrounding himself with memories to remind him of
when life was good and worth living. Now presented before him was an opportunity
to start again, and the thought scared him.

Yet as the minutes passed, the realisation that he couldn't watch this girl
crying came to him. The foolish feeling he had earlier hadn't dispelled, and
burned stronger than ever. It spread to his cheeks and made him go bright red
like a tomato.

``Well, I could do with an outing, and my old friends from Tenebar always keep a
seat or two free at their meals. I suppose it would be no burden if you wanted
come with me and check the shops there for an elixir store.'' When he stopped,
he felt a huge pressure being lifted and finally breathed out, not noticing just
how tense he'd become.

``Really?!'' shouted Trixie, loud enough that Gorn winced and massaged his ear.
''Thank you, thank you mister! I can hardly believe it! My brother will be OK!
Thank you, thank you!'' Trixie was jumping at him and hugging him -- quite
honestly she hadn't expected her `strategy' of crying and begging to work.

For the first time in twenty years, Gorn smiled a broad, genuine smile. ``That's
alright, that's alright, ha ha -- come now, don't be so hasty, I've done nought
for you yet.''

Ah-hum-- my whool
