% vim: spell : ft=tex
\scenesep

\section{Scrabbling for Retorts}

``You have an amusing talent for mispronouncing words longer than your name,''
taunted Gorn. Trixie had been quite relentless with personal jabs since they had
left, and he thought it high time for some payback.

``Sh-shut up! My mum always said I spoke good! N-No, is it well...?'' Trixie
blushed and floundered as she heard Gorn's words.

``Hah hah! And here I thought Little Miss Perfect outshone me in everything.
Can you muster the words to form a retort?''

``Re-retort?'' Trixie froze -- was that a word? \textit{Thinking about it,
'tort' isn't a word, so I bet re-tort isn't either. He's trying to make me slip
up!} she thought. \textit{I shan't let him have the best of me!} She drew
herself upright and took a confident stance. ``Hmph, is that your best trick?
Making up words to trip me up? I didn't expect much else from someone like
you!''

``Oh, but it is a word, and what you just said to me is one! How about this: can
you tell me what you're doing if you accumulating riches?''

Hack-you-mulating britches? ``W-well, it's...'' answered Trixie.

``Hahahahaha! Revenge truly is sweet.'' He laughed heartily and started reeling
off uncommon words and phrases. Though Trixie tried her hardest it quickly
became clear to them both that she was not up to scratch.

``Dear me, you're not too adept at this, hm?" Gorn said with a cruel grin on his
face. It crinkled his cheeks and made him look like he had just finished
plotting world domination.

``W-well it doesn't help that I can't write!'' shouted Trixie in embarrassed
exasperation.

``Hm? You... weren't ever taught literacy?''

She grumbled. ``Mum always said it wasn't useful for girls so they -- I mean my
parents, only taught my brother.''
