% vim: spell : ft=tex
\scenesep

\section{Forming a Balanced Party}

``So you're a... gungs-man?'' Trixie always felt silly trying to say new words.

``Gunsmith,'' corrected Gorn with a slight tut, ``and I should add a mighty good
one at that. The army decided giving me a sword was an exercise in time wasting,
so before long I offered a gun and sent off to learn how it worked.''

``A 'gun'?... Was that the metal thing that you were wearing in that one
portrait? How does it work? It looked like two rods of metal and wood put
together.''

``Ohoh, they are much, much more amazing than that! When I learned how to use
one, they were only being tested in a few cities, since most places consider
researching magic a better use than developing guns. Even now they are just as
rare, since they take a certain skill to use. That is a skill I most definitely
have!'' He laughed heartily to himself and continued. ``You want me to show you
the gun in action, yes? Here, this clearing should make it easy to see.'' He
pointed yonder a few yards to a circular clearing covered with foot's depth of
leaves and enclosed on most sides by trees. They diverted from the trail, Trixie
making sure to kick up leaves with every step.

Gorn led Trixie to the centre of the clearing and revealed the gun clipped to
his belt, previously concealed by the rest of his clothes. It was in a neat
holster which also held a bag on the side. He unclipped it and whipped the gun
out in a exaggerated flourish , which drew an ``ooh'' from Trixie. She had been
right: it was essentially a hollow, shaped metal rod connected to a curved,
polished wooden handle. There were two 'switches' on it: one above the handle on
the metal (facing the wielder) and another at the bend where the two materials
met. On the other side of the bend the gun was enlarged, and there was a closed
slot on the top.

Next he opened the bag and took out a small handful of pellets from it. While
talking, he opened the top of the gun and dropped pellets into it with a
precision Trixie could definitely respect.

``Guns are very advanced weapons -- that's no boast. Put simply... you know how
you use a slingshot, by pulling back a stone and letting go?'' Trixie nodded.
``Mm. It's like that, but everything is done for you, and the stones are fired
at an incredible speed.''

''Every time you want to use one, you have to prepare. First, you have to load
pellets into it, like I just did. With that done, you need to check that there
is enough powder in the gun -- I'll explain that in a bit. Next you pull back
the switch at the top here. Inside it's connected to a little hammer, which when
you click the trigger twangs back to place like a slingshot, hitting the powder
which makes a small explosion -- a bang -- and propels propels the pellet
forwards lightning fast!`` He was practically jumping in Trixie's face with
excitement.
